\section{Motivation}
\label{section_intro_motivation}

Graph theory is a fundamental field of mathematics with significant relevance in
computer science due to its ability to model relationships between objects.
One of the key challenges in computer science is graph traversal and exploration, which involves systematically navigating through the nodes of a graph
with a specific purpose. This topic has practical applications across diverse fields, such as network routing, robotics, procedural generation, electronics design, and more.

When considering the complexities and time constraints imposed by real-world environments,
graph exploration must be expanded to consider multi-agent systems. In such systems, multiple
autonomous agents collaborate to explore graphs, aiming to distribute tasks to achieve optimal efficiency. However, communication strategies
on these systems are challenging, as they need to balance the trade-off between the amount of information shared among agents
versus the quality of the solution. In other words, while communication can allow
agents to speed up their exploration, it may cost time and/or energy.

Various versions of this problem have been explored in research. 
One such approach, discussed by \citen{Kivelevitch2010}, proposed a generalization of Tarry's Algorithm with significant emphasis on minimizing data transfer.
Nevertheless, this solution is limited to mazes and does not extend to general graphs.

Despite the previously mentioned research, the concept of zero-communication exploration has not been
concretely established in the literature. We believe this gap is significant, as practical situations might involve
scenarios where communication is limited or impossible due to bandwidth limitations or energy consumption, such as deep-sea exploration,
search with energy-limited agents, or high-efficiency state space search. 

This work aims to address this gap by presenting a continuation
and expansion of a method initially developed for perfect maze exploration \cite{Naeem2021} as discussed by \citen{Arthur2023}.
Building upon this groundwork, the research extends the method to accommodate diverse graph structures by removing dependencies on specific projects. 
General improvements, such as structuring the exploration into well-defined and extensible classes
and incorporating built-in testing, strive to make the development process more versatile and robust, paving the way for broader applications in multi-agent systems.


\section{Objective}
\label{section_intro_objective}

This study aims to propose a viable algorithm for graph exploration by multi-agents, specifically targeting the identification of a goal node.
A previous paper by \citen{Arthur2023} discussed an approach for perfect maze exploration, which can be modeled as a tree, a connected acyclic undirected graph.
Expanding the proposed algorithm to connected cyclic graphs could allow further discussion and contribute to research in real-world applications 
such as robotics, as well as in the theoretical analysis of parallelism and communication between agents.

\section{Definitions}
\label{section_intro_definitions}

This section aims to define key concepts in graph theory and
multi-agent exploration that are essential for understanding the context 
and methodology of our research, ensuring clarity and consistency in the subsequent discussions.

\subsection{Graph}
\label{section_definitions_graph}

Graphs are structures in mathematics and computer science used to represent
relationships between pairs of objects. According to \citen{Manber1989}, a graph
$G=(V,E)$ is defined as a set $V$ of vertices (or nodes) and a set $E$ of edges,
that connect pairs of vertices. 

\subsubsection{Common Nomenclature}

In graph theory, the basic terminology includes the following components:

\begin{itemize}
    \item Vertex (Node): The fundamental unit of a graph, representing an object or a point.
    \item Edge: A connection between a pair of vertices, representing a relationship between them.
    \item Adjacency: Two vertices $v$ and $w$ of a graph $G$ are adjacent if there is an edge $vw$ joining them, and the vertices $v$ and $w$ are then incident with such an edge. \cite{West2018}
    \item Degree: Degree of a vertex $v$ of $G$ is the number of edges incident with $v$. \cite{West2018}
    \item Path: A path in a graph $G$, as defined by \citen{West2018}, is a finite sequence of edges of the form $v_0v_1$, $v_1v_2$, ... in which any two consecutive edges are adjacent, all edges are distinct and all vertices $v_0$, $v_1$, ..., $v_m$ are distinct (except, possibly, $v_0 = v_m$).
    \item Cycle: A path where $v_0 = v_m$ and with at least one edge. \cite{West2018}
\end{itemize}

\subsubsection{Key Properties}

A few key properties of graphs that interest us are:

\begin{itemize}
    \item Connectivity: A graph is connected if and only if there is a path between each pair of vertices. \cite{West2018}
    \item Acyclicity: A graph is acyclic if it has no cycles. A tree is an acyclic connected graph.
\end{itemize}

\subsubsection{Traversal}

Graph traversal is the process of visiting all the vertices in a graph in a systematic manner. Two fundamental algorithms for graph traversal are:

\begin{itemize}
    \item Breadth-first search (BFS): Expands the frontier between discovered and undiscovered vertices uniformly across the breadth of the frontier. \cite{Manber1989}
    \item Depth-first search (DFS): Explores edges out of the most recently discovered vertex $v$ that still has unexplored edges leaving it. \cite{Manber1989}
    \item Tarry's Algorithm: Tarry's Algorithm is used to traverse the entire maze, or graph, in a depth first fashion, where each edge is travelled twice, and the agent finishes the motion at the same initial vertex it started from.\cite{Kivelevitch2010} This algorithm is described in the context of a physical maze, where the agent must physically move between adjacent nodes.
    It was first described over botanical mazes built as amusements for the XIX century aristocracy.
\end{itemize}

\subsection{Agent}
\label{section_definitions_agent}

An agent in maze exploration, as defined by \citen{Kivelevitch2010}, 
is an entity able to move within the maze in any direction as long as it does not encounter obstacles.

In the context of graph exploration, this concept extends to an agent's ability to traverse
edges between vertices within the graph structure. Each agent acts independently,
making decisions based on its individual memory and the local information available at its current vertex and its adjacent edges.


\subsection{Mixed Radix}
\label{section_definitions_mixed_radix}

A mixed radix system is a positional numerical system in which the numerical base for each digit
varies. This allows for more flexible representation of numbers,
accommodating various scales within the same numerical framework.

One mathematical approach for representing mixed radix numbers can be found in \citen{Arndt2011},
which establishes a comprehensive arithmetical method for manipulating them.  However,
for the specific subset of real numbers within the interval [0, 1], a more specialized approach is utilized, as described by \citen{Arthur2023}.

In this context, the mixed radix representation $A=[a_{0},a_{1},a_{2},...,a_{n-1}]$ 
of a number $x$ with respect to a radix vector $M=[m_{0},m_{1},m_{2},...,m_{n-1}]$,
where $x \in [0,1]$, is given by:

\begin{equation}
	x = \sum_{k=0}^{n-1} a_{k} \prod_{j=0}^{k} \frac{1}{m_j}
\end{equation}
where $a_j$ are non-negative integers, $m_j$ are integers such that $m_j \geq 2$, and $0 \leq a_j \leq m_j$. \cite{Arthur2023}


For instance, if $x$ is represented by $0.2_{3}1_{2}1_{4}0_{3}1_{5}$, and considering that $a_{i}$ is on the left of $a_{i+1}$, $x$ might be transformed to the decimal base by the following steps:

\begin{align}
& x=2_{3}1_{2}1_{4}0_{3}1_{5}\\
& A=[2,1,1,0,1]\\
& M=[3,2,4,3,5]\\
& n=5\\
& x = \sum_{k=0}^{4} a_{k} \prod_{j=0}^{k} \frac{1}{m_j} \approx 0.8777778
\end{align}

\subsubsection{Extending Mixed Radix with Unary Digits}
\label{section_definitions_unary_mixed_radix}

In our study, we extended the mixed radix system to include unary digits,
which are used to represent steps in a sequence where no meaningful decisions are made.
These unary digits do not contribute to the numerical value and can be omitted in the conversion to standard numerical forms.

Within our framework, the mixed radix representation $A=[a_{0},a_{1},a_{2},...,a_{n-1}]$ 
of a number $x$ with respect to a radix vector $M=[m_{0},m_{1},m_{2},...,m_{n-1}]$,
where $x \in [0,1]$, is given by:

Let  $U = \{ k \ |\ m_k \neq 1 \} $ be the set of indices where the base \( m_k \) is not unary.

\begin{equation}
    \label{eq:unary_mixed_radix}
	x = \sum_{k \in U} u_{k} \prod_{j=0}^{k} \frac{1}{m_j}
\end{equation}
where $a_k$ are non-negative integers, $m_j$ are integers such that $m_j \geq 1$, and $0 \leq a_j \leq m_j$.

Consider the mixed radix representation $x=0.2_{3}I_11_{2}I_1I_11_{4}0_{3}1_{5}$, where $I_1$ represents the unary digit and each $a_{i}$ is on the left of $a_{i+1}$. We can transform
$x$ to the decimal base using the following steps:

\begin{align}
    & x=2_{3}I_11_{2}I_1I_11_{4}0_{3}1_{5}\\
    & A=[2,I,1,I,I,1,0,1]\\
    & M=[3,1,2,1,1,4,3,5]\\
    & U=[0,2,5,6,7]\\
    & x = \sum_{k \in U} a_{k} \prod_{j=0}^{k} \frac{1}{m_j} \approx 0.8777778
\end{align}
